% cv-us.tex
% $Id: cv-us.tex,v 1.28 2006/12/12 22:53:52 jrblevin Exp $
%
% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2006 Jason Blevins
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents, however, I do ask that you
% please leave this notice and the above URL in the source code if you
% choose to redistribute this file.
%
% Jason R. Blevins <jrblevin@sdf.lonestar.org>
% http://jrblevin.freeshell.org
% Durham, December 12, 2006
%
%%---------------------------------------------------------------------------%
%
% Notes:
%
% * Don't forget to change `pdfauthor' and `keywords' in the \hypersetup
%   section below.
%
% * To create a new page use: \newpage \opening
%
% * res.cls includes an \address{} command which can be used up to twice,
%   but my address is too long for the format it uses.
%
% * Alternate documentclass statement to put headings in margin:
%   \documentclass[margin,line,11pt,final]{res}
%
% * Can divide publication/presentation list into subsections by year:
%   \section{\bf\small\hspace{8mm}2006}
%
%%----------------------------------------------------------------------------%

\documentclass[overlapped,line,letterpaper]{res}

\usepackage{ifpdf}

\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi

\hypersetup{
  letterpaper,
  colorlinks,
  urlcolor=black,
  pdfpagemode=none,
  pdftitle={Curriculum Vitae},
  pdfauthor={Niranjan Balasubramanian},
  pdfsubject={Curriculum Vitae}
}

%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

%---------------------------------------------------------------------------

\name{Niranjan Balasubramanian}

\begin{resume}
\begin{ncolumn}{2}
Research Assistant Professor    & E-mail:  niranjan@cs.stonybrook.edu \\
Stony Brook University		& Phone: $631\ 632\ 8470$\\
						& Webpage: http://www3.cs.stonybrook.edu/$\sim$niranjan/
 \end{ncolumn}
%---------------------------------------------------------------------------
\section{\bf Research Interests}
\vspace{0.1in}
{\bf Natural Language Processing} \\
Event extraction, Knowledge Extraction, and Question Answering.

{\bf Information Retrieval}\\
 Performance estimation, Query-dependent strategies, and Mobile search.

\section{\bf Education}
\vspace{0.1in}
{\bf Ph.D}, Computer Science -- University of Massachusetts Amherst, July 2011.\\
{\bf M.S.}, Computer Science -- University at Buffalo (SUNY), July 2003.\\
{\bf B.Eng}, Computer Science -- Shanmugha College of Engineering, Tamilnadu, India, May 2001.\\

\section{\bf Work Experience}
\vspace{0.1in}
\begin{format}
\title{l}\location{r}\\
\employer{l}\dates{r}\\
%\employer{l}\location{r}\\
\body\\
\end{format}
\title{Research Assistant Professor} \employer{Department of Computer Science and \\Biomedical Informatics}
\location{{\bf Stony Brook University}}
\dates{Jan 2015 -- Present.}
\begin{position}
\end{position}
\title{Postdoctoral Fellow} \employer{Mentor: Oren Etzioni}
\location{{\bf University of Washington}}
\dates{July 2011 --  Dec 2014}
\begin{position}
{\em Event Modeling and Question Answering using Open Information Extraction.}
\end{position}
\title{Research Assistant}
\employer{Advisor: Prof. James Allan}
\location{{\bf University of Massachusetts}}
\dates{2006 -- 2011}
\begin{position}
{\em Query dependent strategies in Information Retrieval}
\end{position}
%\title{Research Intern}
%\employer{Mentors: Vitor Carvalho and Giridhar Kumaran}
%\location{{\bf Microsoft Research}}
%\dates{Summer 2009}
%\begin{position}
%{\em Improving web search performance for long queries.}
%\end{position}
%\title{Research Intern}
%\employer{Mentor: Silviu Cucerzan}
%\location{{\bf Microsoft Research}}
%\dates{Summer 2008}
%\begin{position}
%{\em Generating wikipedia like pages for entities.}
%\end{position}
%\title{Research Intern}
%\employer{Mentor: Arkady Borkovsky}
%\location{{\bf Yahoo! Applied Research}}
%\dates{Summer 2008}
%\begin{position}
%{\em  Statistical models for Question retrieval.}
%\end{position}

\title{Software Engineer}
\employer{Center for Natural Language Processing\\
Manager: Prof. Elizabeth D. Liddy}
\location{{\bf Syracuse University}}
\dates{2003--2006}
\begin{position}
{\em Development of Question Answering, and Information extraction tools.}
\end{position}

\section{\bf Teaching}
\begin{enumerate}
\item Grad: Advanced Topics in Computational Linguistics, Fall 2015, Stony Brook University.
\item Grad: Introduction to Natural Language Processing, Spring 2015, Stony Brook University.
%\item {\bf Teaching Assistant:} Information Retrieval by Prof. James Allan, CS Univ. of Massachusetts.
%\item Guest Lecture: Machine Learning for IR, Fall 2014, University of Washington, Tacoma.
\end{enumerate}

\section{\bf Conference Publications} 
\vspace{0.2in}
\begin{enumerate}
\item {\bf [EMNLP 2015]} Exploring Markov Logic Networks or Question Answering\\
	Khot, T., Balasubramanian, N., Eric Gribkoff, Sabharwal, A., Clark, P., Etzioni, O.\\
	Conference on Empirical Methods in Natural Language Processing.
		
\item {\bf [EMNLP 2013]} Generating Coherent Event Schemas at Scale.\\
	Balasubramanian, N., Soderland, S., Mausam, and Etzioni, O.\\
	Conference on Empirical Methods in Natural Language Processing.
	
\item {\bf [CoNext 2012]} FindAll: A Local Search Engine for Mobile Phones.\\
	Balasubramanian, A., Balasubramanian, N., Huston, Samuel., Metzler, Donald.\\	 
	ACM CoNext conference.

\item {\bf [SIGIR 2010]} Exploring Reductions for Long Web Queries.\\
	Balasubramanian, N., Kumaran, G., and Carvalho, V.\\
	ACM SIGIR Conference.

\item {\bf [SIGIR 2010]} Learning to Select Rankers.\\
	Balasubramanian, N. and Allan, J.\\
	A poster paper at ACM SIGIR Conference.
	
\item {\bf [SIGIR 2010]} Predicting Query Performance on the Web.\\
	Balasubramanian, N., Kumaran, G., and Carvalho, V.\\
	A poster paper at ACM SIGIR Conference.

\item {\bf [ICSC 2010]} Topic Pages: An Alternative to the Ten Blue Links.\\
	Balasubramanian, N. and Cucerzan, S.\\
	IEEE Conference on Semantic Computing {\bf (Among top 5 papers selected for IJSC journal.)}

\item {\bf [CIKM 2009]} Automatic Generation of Topic Pages Using Query-based Aspect Models.\\
	Balasubramanian, N. and Cucerzan, S.\\
	A short paper at ACM Conference on Information and Knowledge Management

\item {\bf [IMC 2009]} Energy Consumption in Mobile Phones: A Measurement Study and Implications for Network Applications.\\
	Balasubramanian, N., Balasubramanian, A. and Venkataramani, A.\\
	ACM Internet Measurement Conference.
	
\item {\bf [SPIRE 2009]} Syntactic Query Models for Restatement Retrieval.\\
	Balasubramanian, N. and Allan, J.\\
	String Processing and Information Retrieval Conference.
	
\item {\bf [SIGIR 2007]} A Comparison of Sentence Retrieval Techniques.\\
	Balasubramanian, N., Allan, J. and Croft, W. B.\\
	A poster at ACM SIGIR Conference.

%\item {\bf [AAAI 2005]} Improved Document Representation for Classification Tasks for the Intelligence Community.\\
%	Yilmazel, O., Symonenko, S., Balasubramanian, N., Liddy, E.D.\\
%	Proceedings of AAAI Spring Symposium Series.

\end{enumerate}
\section{\bf Journal publications}
\vspace{0.2in}
\begin{enumerate} 
\item {\bf [IJSC 11]} Beyond Ranked Lists in Web Search: Aggregating Web Content in Topic Pages.\\
	Balasubramanian, N., and Cucerzan, S.\\
	International Journal of Semantic Computing, 2011.
\end{enumerate}

\section{\bf Workshop publications}
\begin{enumerate}
\vspace{0.2in}

\item {\bf [K-CAP 2015]} Semantic Role Labeling for Process Recognition Questions\\
	Louvan, S., Naik, C., Lynn, V., Arun, A., Balasubramanian, N., and Clark, P.\\
	K-CAP Scientific Knowledge Workshop 2015.
	
\item {\bf [StarAI 2015]} Markov Logic Networks for Natural Language Question Answering.
	Khot, T., Balasubramanian, N., Eric Gribkoff, Sabharwal, A., Clark, P., Etzioni, O.\\
	International Workshop on Statistical Relational AI.
	
\item {\bf [AKBC 2014]} Automatic Construction of Inference-Supporting Knowledge Bases	{\bf[Best Paper]}\\
	Clark, P., Balasubramanian, N., Bhakthavatsalam, S., Humphreys, K., Kinkead, J., Sabharwal, A., Tajford, O.\\ 	
	Automatic Knowledge Base Construction and Web-scale Knowledge Extraction 2014.

\item {\bf [AKBC 2013]} A Study of the AKBC/Requirements for Passing an Elementary Science Test. \\
	Clark P., Harrison P., Balasubramanian N.\\ 
	 Automatic Knowledge Base Construction and Web-scale Knowledge Extraction at CIKM 2013.

\item {\bf [AKBC 2012]} Rel-grams: A Probabilistic Model of Relations in Text.\\ 
	Balasubramanian, N., Soderland, S., Mausam, Etzioni, O.\\ 
	 Automatic Knowledge Base Construction and Web-scale Knowledge Extraction at NAACL 2012.

\item {\bf [AKBC 2012]} Constructing a Textual KB from a Biology TextBook.\\
	 Clark, P., Harrison, P., Balasubramanian, N., Etzioni, O.\\
	 Automatic Knowledge Base Construction and Web-scale Knowledge Extraction at NAACL 2012.

\item {\bf [NW-NLP 2012]} Answering Biology Questions using Textual Reasoning.\\
	Clark, P., Harrison, P., Balasubramanian, N.\\
	Pacific Northwest Regional NLP Workshop 2012. 

%\item {\bf [NESCAI 2010]} Cost-Effective Combination of Multiple Rankers: Learning When Not To Query.\\
%	Balasubramanian, N., Bendersky, M. and Allan, J.\\
%	A poster at the NESCAI Student Colloquium, 2010

\end{enumerate}

\section{Technical Reports}
\begin{enumerate}
\item {\bf[2012]} “Out of the Box” Information Extraction: a Case Study using Bio-Medical Texts.\\
	Balasubramanian, N., Soderland, S., Mausam, Etzioni, O., and Bart, R.\\
	Technical Report (UW-CS-2012-xxx) in Computer Science, University of Washington.		
\item {\bf[2011]} Modeling Relative Effectiveness to Leverage Multiple Ranking Algorithms.\\ 
	Balasubramanian, N. and Allan, J.\\
	CIIR Technical Report (IR-xxx) in University of Massachusetts Amherst.
\item {\bf[2009]} Energy Aware Search from Mobile Phones.\\
	Balasubramanian, N., Venkataramani, A. and Allan, J.,\\
	CIIR Technical Report (IR-706) in University of Massachusetts Amherst.		
\item {\bf[2009]} Energy Consumption in Mobile Phones: Measurement, Design Implications, and Algorithms.\\
	Balasubramanian, N., Balasubramanian, A., and Venkataramani, A.\\
	Technical Report (UM-CS-2009-022) in Computer Science, University of Massachusetts Amherst.
\end{enumerate}

\section{Invited Contributions}
\begin{enumerate}
\item {\bf[2010]} Online Feature Selection for Information Retrieval.\\
	Balasubramanian, N., Kumaran, G., Carvalho, V. and Allan, J.\\
	Feature Generation and Selection Workshop for Information Retrieval, SIGIR 2010.
\end{enumerate}

\section{\bf Theses}
\begin{enumerate}
\item {\bf Ph.D. [2011]} Query-dependent Selection of Retrieval Alternatives.\\
	Advisor: James Allan\\
	University of Massachusetts Amherst.

\item {\bf Masters [2003]} Automatic Acquisition of Concept Hierarchies in an Integrated Information Retrieval/Information Extraction framework.\\
	Advisor: Rohini Srihari\\
	University at Buffalo.
	
\end{enumerate}

\section{\bf Invited talks}
\begin{enumerate}  
\item {\bf University at Buffalo} - Open Event Schemas, CS Colloquium Series, October 2013.
\item {\bf Decide.com} - Machine Learning for Information Retrieval, March 2012.
\item {\bf University of Washington} - Machine Learning for Information Retrieval, AI Seminar, Feb 2012.
\item {\bf University of Waterloo} - Query-dependent Selection of Retrieval Alternatives, March 2010. 
\item {\bf University at Buffalo} - Query-dependent Selection of Retrieval Alternatives, March 2010. 
\end{enumerate}


\section{\bf Services and Awards}
\vspace{0.2in}
\begin{enumerate}
\item {\bf Reviewing:} 
\begin{itemize}
\item {\bf IR} -- SIGIR 2015, ACL 2015, 2012-14 posters, CIKM 2012-13
\item {\bf NLP} -- EMNLP 2012-13, AAAI 2012-13
\end{itemize}
\item {\bf Travel Award}: SIGIR 2010.
\item {\bf Graduate Student Representative, UMass CS}: 2010. 
\end{enumerate}

\end{resume}


\end{document}

%%===========================================================================%%
